Analysis of competitive surfing tournaments with generalized Bradley-Terry likelihoods

### 2022-09-27 inst/jss_4382.tex
fixes #159

>>>>

\textcolor{blue}{Response: the pattern has been removed as suggested,
  all functions exported are exported explicitly.  However, it is not
  clear who ``the user" is.  Currently, the users are restricted to
  myself and a bunch of graduate students, who are mostly working on
  applying hyper2 constructions to their own pet datasets; this group
  of users needs to see similar work that they can modify for their
  own projects.  But the output of \verb+help(package = "hyper2")+ is
  now restricted only to functions that might be of interest to users.
  }
